MacLeish

### 2018-03-27 README.Rmd
updated NEWS and README

```{r, eval=FALSE, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = macleish_layers[["boundary"]], 
              weight = 1, fillOpacity = 0.1) %>%
  addPolygons(data = macleish_layers[["buildings"]], 
              weight = 1, popup = ~ name) %>%
  addPolylines(data = macleish_layers[["trails"]], 
               weight = 1, color = "brown",
               popup = ~ name) %>%
  addPolylines(data = macleish_layers[["streams"]], 
               weight = 2) %>%
  addMarkers(data = subset(macleish_layers[["landmarks"]], grepl("Met", Label)), 
             popup = ~Label)
```

>>>>

```{r, eval=FALSE, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = macleish_layers[["boundary"]], 
              weight = 1, fillOpacity = 0.1) %>%
  addPolygons(data = macleish_layers[["buildings"]], 
              weight = 1, popup = ~ name) %>%
  addPolylines(data = macleish_layers[["trails"]], 
               weight = 1, color = "brown",
               popup = ~ name) %>%
  addPolylines(data = macleish_layers[["streams"]], 
               weight = 2) %>%
  addMarkers(data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
             popup = ~Label)
```
